Galois Transformers and Modular Abstract Interpreters:\\ Reusable Metatheory for Program Analysis

### 2014-11-13 writeup/pldi15.tex
Spelling in abstract.

\par We solve the problem of systematically constructing static
analyzers by introducing the notion of a \emph{Galois transformer}, a
monad transformer that satisfies the properties of a Galois
connection.  In concert with a monadic interpreter, we are able to
define a library of monad transfomers implementing classic context,
path, and heap (in-)senstive building blocks which can be composed
together to realize a program analysis monad, \emph{independent of the
  language being analyzed}.

\par Significantly, a Galois transformer can be proved sound once and
for all, making it a reusable analysis component.  As new analaysis
features and abstractions are developed and mixed in, soundness proofs
need not be reconstructed as the composition of a monad transfomer
stack is sound by virtue of its consituents.  We believe Galois
transformers provide a viable foundation for resuable and composable 
metatheory for program analysis.
\end{abstract}
% }-}

>>>>

\par We solve the problem of systematically constructing static
analyzers by introducing the notion of a \emph{Galois transformer}, a
monad transformer that satisfies the properties of a Galois
connection.  In concert with a monadic interpreter, we are able to
define a library of monad transformers implementing classic context,
path, and heap (in-)sensitive building blocks which can be composed
together to realize a program analysis monad, \emph{independent of the
  language being analyzed}.

\par Significantly, a Galois transformer can be proved sound once and
for all, making it a reusable analysis component.  As new analysis
features and abstractions are developed and mixed in, soundness proofs
need not be reconstructed as the composition of a monad transformer
stack is sound by virtue of its constituents.  We believe Galois
transformers provide a viable foundation for reusable and composable 
metatheory for program analysis.
\end{abstract}
% }-}
